```{r}
#| label: setup
#| include: false

library(beepr)
library(cffr)
library(codemetar)
library(groomr) # https://github.com/danielvartan/groomr
library(here)
library(lubritime)
library(readr)
library(rutils) # https://github.com/danielvartan/rutils
library(stringr)
```

# lubritime

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check.yaml](https://github.com/danielvartan/lubritime/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/danielvartan/lubritime/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/danielvartan/lubritime/branch/main/graph/badge.svg)](https://app.codecov.io/gh/danielvartan/lubritime?branch=main)
[![License: MIT](https://img.shields.io/badge/license-MIT-green)](https://choosealicense.com/licenses/mit/)
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](CODE_OF_CONDUCT.md)
<!-- badges: end -->

## Overview

`lubritime` is an extension for the [lubridate](https://github.com/tidyverse/lubridate) package from [tidyverse](https://www.tidyverse.org/), adding new features to deal with temporal objects.

Please note that `lubritime` is not related in any way with `Posit/RStudio` or the `lubridate` developer team.

## Installation

You can install `lubritime` using the [`remotes`](https://github.com/r-lib/remotes) package:

``` {r}
#| eval: false

remotes::install_github("danielvartan/lubritime")
```

## License

[![License:
MIT](https://img.shields.io/badge/license-MIT-green)](https://opensource.org/license/mit/)

`lubritime` code is released under the [MIT license](https://opensource.org/license/mit/).

## Contributing

We welcome contributions, including bug reports. Take a moment to review our [Guidelines for Contributing](https://danielvartan.github.io/lubritime/CONTRIBUTING.html).

<br>

Become an `lubritime` supporter!

Click [here](https://github.com/sponsors/danielvartan) to make a donation. Please indicate the `lubritime` package in your donation message.
